Diversification of Australian blind snakes

### 2022-10-04 manuscript.Rmd
update new subheading

## Reconstruction of Australian paleo climate 
<!-- Consult Alex Skeels -->
Two paleographic digital elevation models (DEMs) providing paleotopography at resolution of 1&deg; x 1&deg; and 5 myr resolution  were obtained from Scotese (2021) [@scoteseAtlas2021] and Straume et al (2020) [@straumeGlobal2020]. We projected the paleoenvironmental reconstructions into an equal-area Behrmann projection of 110km x 110km following methods described in Hagen et al (2021) @hagenGen3sis2021. From the projected data we extracted temperature and aridity values across all grid cells that fall within Sahul by manually drawing a polygon that encompassed the continent from 40 mya to the present-day (\@ref(fig:fig-aus-region).

@@

## Biome transitions and current distributions
- The earliest biome transition was from tropical grassland into XXX by XX MYA (95% HPD: XX – XX). 
- Subsequent splits show transitions the arid zone coinciding with with the onset of aridification between 20 – 10 MYA. 
- Most species are still found in tropical grasslands, but also in arid zone. 
- Greatest number of species can be found in ...

- Range expansion was important for diversification ...

- Topography dyanmics [@brazModelling2021]

@@

>>>>

## Reconstruction of Australian paleo climate 
<!-- Consult Alex Skeels -->
Two paleographic digital elevation models (DEMs) providing paleotopography at resolution of 1&deg; x 1&deg; and 5 myr resolution  were obtained from @scoteseAtlas2021 and @straumeGlobal2020. We projected the paleoenvironmental reconstructions into an equal-area Behrmann projection of 110km x 110km following methods described in @hagenGen3sis2021. From the projected data we extracted temperature and aridity values across all grid cells that fall within Sahul by manually drawing a polygon that encompassed the continent from 40 mya to the present-day (\@ref(fig:fig-aus-region).

@@

## Biome transitions and current distributions
- The earliest biome transition was from tropical grassland into XXX by XX MYA (95% HPD: XX – XX). 
- Subsequent splits show transitions the arid zone coinciding with with the onset of aridification between 20 – 10 MYA. 
- Most species are still found in tropical grasslands, but also in arid zone. 
- Greatest number of species can be found in ...
- Range expansion was important for diversification ...
- Topography dyanmics [@brazModelling2021]

@@

## Arid vs. non-arid speciation
